---
title       : Data Products
subtitle    : Modelling horsepower, number of cylinders, and weight to predict mpg
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Synopsis

The present application is using a linear model with horsepower, number of cylinders, and weight as input parameter
and uses the inputed values to predict the miles per gallon of a vehicle having such characteristics. Please, note that 
inputed weight is converted dividing it by 1000 to comply with mtacars dataset requirements. The choice on cylinder number is likewise limited via radio button to the choices allowed by mtcars dataset (4, 6 or 8).

Part1: Shiny Application

* URL: https://coursera-data-products.shinyapps.io/Developing-Data-Products-shiny-and-slidify--master/ 
* A shiny-App detailing the effect of horsepower, number of cylinders, and weight on miles per gallon of a vehicle. 

--- .class #id 

## mtcars dataset - Description

### Data Source: Motor Trend magazine (Car Road Tests) - 1974

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 different automobiles (1973-74 models).


```{r data}
library(datasets)
head(mtcars, 3)
```

--- .class #id

## Features

* The application predict MPG basing upon input variables:
  * Horse Powers
  * Weight
  * Number of cylinders
* The variables are visualized using a 3D scatterplot
* User can change the input variables and verify the predicted MPG as well as the relative position of his input in the 3D scatterplot

--- .class #id

## Sample 3D Plot showing the relationship between variables 

```{r sample_plot, echo=FALSE}
library(scatterplot3d)
library(datasets);
# create column indicating point color
mtcars$pcolor[mtcars$cyl==4] <- "red"
mtcars$pcolor[mtcars$cyl==6] <- "blue"
mtcars$pcolor[mtcars$cyl==8] <- "darkgreen"
with(mtcars, {
  s3d <- scatterplot3d(hp, wt, mpg,        # x y and z axis
                       color=pcolor, pch=19,        # circle color indicates no. of cylinders
                       type="h", lty.hplot=2,       # lines to the horizontal plane
                       scale.y=.75,                 # scale y axis (reduce by 25%)
                       main="3-D Scatterplot Example 4",
                       xlab="Horse power",
                       ylab="Weight (lb/1000)",
                       zlab="Miles/(US) Gallon")
  s3d.coords <- s3d$xyz.convert(hp, wt, mpg)
  text(s3d.coords$x, s3d.coords$y,     # x and y coordinates
       labels=row.names(mtcars),       # text to plot
       pos=4, cex=.5)                  # shrink text 50% and place to right of points)
  # add the legend
  legend("topleft", inset=.05,      # location and inset
         bty="n", cex=.5,              # suppress legend box, shrink text 50%
         title="Number of Cylinders",
         c("4", "6", "8"), fill=c("red", "blue", "darkgreen"))
})
```



